comgen-outline

### 2017-08-10 paper/comgen-paper.Rmd
edit intro

abstract: > 
    Generalizations are central to human understanding yet can be difficult to acquire through direct experience (e.g., learning that a plant is poisonous).
    Language provides simple ways to convey generalizations (e.g., *Birds fly.*), and the language of generalizations is ubiquitous in everyday discourse and child-directed speech.
    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
    The major issue in formalizing *genericity* is in determining the conditions under which such statements are true or false; these conditions are extremely flexible in communicating generalizations. 
    Using a state-of-the-art probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context. 
    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (i.e., *generic language*, e.g., *Birds fly*), events (i.e., *habitual language*, e.g., *John runs*), and causes (i.e., *causal language*, e.g., *The block makes the machine play music.*). Across these divesre domains, we find that our model, and not simpler models, explains the full spectra of endorsements of generalizations in language.
    The model suggests that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.

@@

```{r figure-causals, fig.width=11, fig.height=8, cache = F}
grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,
             layout_matrix = cbind(c(1,1,2)))

>>>>

abstract: > 
    Generalizations are central to human understanding yet can be difficult to acquire through direct experience (e.g., learning that a plant is poisonous).
    Language provides simple ways to convey generalizations (e.g., *Birds fly.*), and the language of generalizations is ubiquitous in everyday discourse and child-directed speech.
    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
    The major issue in formalizing *genericity* is in determining the conditions under which such statements are true or false; these conditions are extremely flexible. 
    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context. 
    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language*, such as *Birds fly*), events (*habitual language*, such as *John runs*), and causes (*causal language*, such as *The block makes the machine play music.*). Across these diverse domains, we find that our model explains the full spectra of endorsements of generalizations in language, while simpler models do not.
    These results suggest that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.

@@

```{r figure-causals, fig.width=11, fig.height=8, cache = T}
grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,
             layout_matrix = cbind(c(1,1,2)))
